Data analysis for employee cluster descriptive statistics

### 2023-08-10 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge") 
```

@@

>>>>

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(sso) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(sso), scales = "free")
```

@@

Majority are freom PBS.
